Developing a Bubble Chamber Particle Discriminator Using Semi-Supervised Learning

### 2018-11-27 documentation/paper.tex
Switched to BibTeX

\usepackage[margin=1in]{geometry}
\usepackage{textcomp}
\usepackage{parskip}
\usepackage{amsmath}
\usepackage{authblk}
\usepackage[backend=biber, style=alphabetic, sorting=ynt]{biblatex}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{caption}
\usepackage{hyperref}

@@

This is used in the banded frequency position correction function $PosCor(\beta _{8}, \chi)$, which corrects $\beta _{8}$ for variations in amplitude which depend on the position of the bubble. $PosCor(\beta _{8}, \chi)$ is used for training several machine learning models throughout this study. Details of its use are in Section \ref{mlp}.

>>>>

\usepackage[margin=1in]{geometry}
\usepackage{textcomp}
\usepackage{parskip}
\usepackage{amsmath}
\usepackage{authblk}
\usepackage[backend=bibtex, style=alphabetic, sorting=ynt]{biblatex}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{caption}
\usepackage{hyperref}

@@

This is used in the banded frequency position correction function $PosCor(\beta _{8}, \chi)$, which corrects $\beta _{8}$ for variations in amplitude which depend on the position of the bubble. $PosCor(\beta _{8}, \chi)$ is used for training several machine learning models throughout this study, because it is expected to alleviate the biases mentioned in Section \ref{og_analysis}. Details of its use are in Section \ref{mlp}.
